Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023

### 2024-09-27 paper/paper.qmd
change the introduction and abstract part in paper. and add some other information in each scripts.

---
title: "Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023"
subtitle: "Analyzing Theft and Assault Trends Across Neighborhoods "
author: 
  - Mingxuan Liu
thanks: "Code and data are available at: https://github.com/MingxuanLiu506/Crime_Rate.git"
date: 09-21-2024
date-format: long
abstract: "This paper focuses on the temporal and spatial trends of burglary and assault crime rates in different urban areas from 2014 to 2023. Through analyzing the data Neighbourhood Crime Rates, it is found that there are significant differences in robbery and attack rates in different regions and different time periods. And crime in some areas continues to increase, while in others it fluctuates or decreases. In addition, it is worth noting that there is also a correlation between population size and assault rates. Based on the research results, this paper provides targeted management schemes and resource reallocation schemes for the government and law enforcement agencies to reduce the community crime rate."
format: pdf
toc: true
number-sections: true
# The toc parameter used to create a table of contents was obtained from
# Quarto documentation:
# https://quarto.org/docs/reference/formats/pdf.html
bibliography: references.bib
---
```{r}
#| echo: false
#| warning: false
#### Preamble ####

@@

Since 2020, the Covid-19 outbreak has intensified this trend. Thefts have spiked in many cities around the world during the pandemic due to economic instability worldwide and reduced social interaction due to lockdown policies [@syamsuddin2021effect]. Toronto's neighbourhoods are no exception, with economic pressures leading to a marked increase in property crime in some neighbourhoods. In addition, population growth is also a factor in the rising crime rate. Population growth increases the opportunity for crime, and areas with higher population density and tight resources have more opportunities for crime [@bettencourt2007growth]. That's because densely populated areas have limited law enforcement resources, and they can't respond to crime suspects everywhere in a short period of time.

In order to further explore the spatio-temporal changes of the crime rate in Toronto, this study obtains the crime data of various communities from 2014 to 2023 according to the method described in @sec-data-overview, especially the data of theft and assault rates. Through these data, this paper analyzes the change trend of crime rates in different communities during these years. The differences between community size and crime rate and the fluctuations in different time periods are discussed. In addition, The research focuses on the dynamic change of crime rate in different communities before and after the epidemic (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates). By assessing these dynamics, this paper aims to inform law enforcement and city planners in Toronto, particularly with regard to resource allocation and crime prevention in high-risk neighbourhoods.

@@

The variables or measurements included in this analysis are "crime type", referring to various forms of crime and violation, which are called THEFTOVER_RATE_year and ASSAULT_RATE_year in the original data. In addition, the "population number" is used as the comparison data, which is called "POPULATION_2023" in the original data.

>>>>

---
title: "Urban Crime Dynamics: Trends in Theft and Assault Over 2014 to 2023"
subtitle: "Analyzing Theft and Assault Trends Across Neighborhoods "
author: 
  - Mingxuan Liu
thanks: "Code and data are available at: https://github.com/MingxuanLiu506/Crime_Rate.git"
date: 09-21-2024
date-format: long
abstract: "This paper focuses on the temporal and spatial trends of burglary and assault crime rates in different neighborhood in Toronto from 2014 to 2023. Through analyzing the data Neighbourhood Crime Rates, it is found that there are significant differences in robbery and attack rates in different regions and different time periods. And crime in some areas continues to increase, while in others it fluctuates or decreases. In addition, it is worth noting that there is also a correlation between population size and assault rates. These findings provide valuable insights for local governments and law enforcement agencies to implement targeted crime prevention strategies, as well as serve as reference examples when similar situations occur in other areas."
format: pdf
toc: true
number-sections: true
# The toc parameter used to create a table of contents was obtained from
# Quarto documentation:
# https://quarto.org/docs/reference/formats/pdf.html
bibliography: references.bib
---
```{r}
#| echo: false
#| warning: false
#### Preamble ####

@@

Since 2020, the Covid-19 outbreak has intensified this trend. Thefts have spiked in many cities around the world during the pandemic due to economic instability worldwide and reduced social interaction due to lockdown policies [@syamsuddin2021effect]. Toronto's neighbourhoods are no exception, with economic pressures leading to a marked increase in property crime in some neighbourhoods, while others show varying fluctuations in trends. In addition, population growth is also a factor in the rising crime rate, which continues to rise in some neighborhoods. Population growth increases the opportunity for crime, and areas with higher population density and tight resources have more opportunities for crime [@bettencourt2007growth]. That's because densely populated areas have limited law enforcement resources, and they can't respond to crime suspects everywhere in a short period of time.

Although there have been studies showing the relationship between crime and economic conditions and population growth, there is still a lack of in-depth research on the dynamics of crime in different communities, especially the dynamic relationship between population density, Covid-19 and crime rates. This study will fill this gap through data analysis. This study obtains the crime data of various communities from 2014 to 2023 according to the method described in @sec-data-overview, especially the data of theft and assault rates. Through these data, this paper analyzes the change trend of crime rates in different communities during these years. The differences between community size and crime rate and the fluctuations in different time periods are discussed. In addition, The research focuses on the dynamic change of crime rate in different communities before and after the epidemic (@fig-theft-rate-trend-2014-to-2023 and @fig-Box-plot-of-theft-rates) and the relationship between population density and crime rates in 2023 (@fig-population-and-assault-rate and @fig-Bar-chart-2023-theft-rates). By assessing these dynamics, this study not only informs law enforcement and urban planners in Toronto, but also in other cities facing similar crime rate challenges, particularly in terms of resource allocation and crime prevention in high-risk neighborhoods.

@@

The variables or measurements included in this analysis are "crime type", referring to various forms of crime and violation, which are called "THEFTOVER_RATE_YEAR" and "ASSAULT_RATE_YEAR" in the original data. In addition, the "population number" is used as the comparison data, which is called "POPULATION_2023" in the original data.
